---
title: "lit-rev"
output:
  pdf_document: default
  html_notebook: default
---

lit review quick exploration.

Search done in Web of Science

Search term used:

TS = ("species distribution" AND model AND predator AND prey)
*TS = topic search

```{r pre-install packages, include=FALSE}
packages <- c("ggplot2") 
source("./src/ipak.R")
ipak(packages)
```

# Load data and remove inapporpriate studies

```{r load raw data}
lrev <- read.csv("./data/sdm-lit-44papers.csv", header = TRUE, stringsAsFactors = FALSE)
lrev <- lrev[!is.na(lrev$Year), ] #remove any rows with no data
t1 <- nrow(lrev) #how many papers did the search find
```

There are a total of 105 papers

## remove studies that aren't origianl research

```{r remove non-suitable studies}
lrev <- subset(lrev, review..comment..opinion..not.an.article. == "no")
t2 <- nrow(lrev) #how many papers remaining
prm <- t1 - t2 #how many papers removed
```

8 papers removed as not original research
97 papers remaining

## remove studies that don't include a predator-prey spatial interaction

```{r remove papers that didnt inc pred-prey spatial interaction}
lrev <- subset(lrev, Does.it.include.predator.prey.interaction.and.distribution == "yes")
t3 <- nrow(lrev) #how many papers remaining
prm <- t2 - t3 #how many papers removed
```

47 papers removed as didn't inc pred-prey spatial interaction
50 papers remaining

# Explore data


## Which biome did the studies occur in

```{r are studies land or water based}
lw <- with(lrev, table(marine..terrestrial..fw))
write.csv(lw, file = "./output/land-water-count.csv")
ggplot(lrev, aes(marine..terrestrial..fw)) + geom_bar() + theme_classic () + labs(x = "Study Location", y = "No. Studies")
```

## what spatial scale did the studies occur at

```{r spatial scale}
lw <- with(lrev, table(Spatial.Scale))
write.csv(lw, file = "./output/spatial-scale.csv")
ggplot(lrev, aes(Spatial.Scale)) + geom_bar() + theme_classic () + labs(x = "Spatial Scale", y = "No. Studies")
```

## what 'region' did the studies occur in

```{r region}
lw <- with(lrev, table(Region))
write.csv(lw, file = "./output/region.csv")
ggplot(lrev, aes(Region)) + geom_bar() + theme_classic () + labs(x = "Region", y = "No. Studies")
```

## what model approach did the studies use

```{r model approach}
lw <- with(lrev, table(Model.Approach))
write.csv(lw, file = "./output/model-approach.csv")
ggplot(lrev, aes(Model.Approach)) + geom_bar() + theme_classic () + labs(x = "Model Approach", y = "No. Studies")
```

## what model family did the studies use

```{r Model Type simplifed}
lw <- with(lrev, table(ModelTypeSimple))
write.csv(lw, file = "./output/ModelTypeSimple.csv")
ggplot(lrev, aes(ModelTypeSimple)) + geom_bar() + theme_classic () + labs(x = "Model Type", y = "No. Studies") + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## what model algoritms did the studies use

```{r Model Algorithm}
malg <- read.csv("./data/model-alg-simple.csv", header = TRUE, stringsAsFactors = FALSE) #models split to one per entry
lw <- with(malg, table(ModelAlgorithmSimple))
write.csv(lw, file = "./output/ModelAlgorithmSimple.csv")
ggplot(malg, aes(ModelAlgorithmSimple)) + geom_bar() + theme_classic () + labs(x = "Model Algorithm", y = "No. Studies") + coord_flip()
```
## what predator class did the studies look at

```{r predator class}
malg <- read.csv("./data/pred-preyclass-simple.csv", header = TRUE, stringsAsFactors = FALSE) #models split to one per entry
lw <- with(malg, table(PredatorClass))
write.csv(lw, file = "./output/PredClass.csv")
ggplot(malg, aes(PredatorClass)) + geom_bar() + theme_classic () + labs(x = "Predator Class", y = "No. Studies") + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## what predator data type did the studies use

```{r predator data}
lw <- with(lrev, table(PredatorDatatypeSimple))
write.csv(lw, file = "./output/PredDataSimple.csv")
ggplot(lrev, aes(PredatorDatatypeSimple)) + geom_bar() + theme_classic () + labs(x = "Predator Data", y = "No. Studies") + coord_flip()
```

## what prey class did the studies use

```{r prey class}
malg <- read.csv("./data/pred-preyclass-simple.csv", header = TRUE, stringsAsFactors = FALSE) #models split to one per entry
lw <- with(malg, table(PredatorClass))
write.csv(lw, file = "./output/PreyClass.csv")
ggplot(malg, aes(PredatorClass)) + geom_bar() + theme_classic () + labs(x = "Prey Class", y = "No. Studies") + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## what prey data type did the studies use

```{r prey data}
lw <- with(lrev, table(PreyDataTypeSimple))
write.csv(lw, file = "./output/PreyDataSimple.csv")
ggplot(lrev, aes(PreyDataTypeSimple)) + geom_bar() + theme_classic () + labs(x = "Prey Data", y = "No. Studies") + coord_flip()
```

# did the studies look at the influence of prey on predator 'distribution' (prey-pred), predator on prey (pred-prey), or co-occurrence (or niche - one study, that possibly shouldn't be included)

```{r prey-pred or pred-prey}
lw <- with(lrev, table(predator.impact.on.prey.or.prey.impacton.on.both))
write.csv(lw, file = "./output/Prey-pred-int.csv")
ggplot(lrev, aes(predator.impact.on.prey.or.prey.impacton.on.both)) + geom_bar() + theme_classic () + labs(x = "Who Drives Who", y = "No. Studies")
```

